---
title: "Interactive Map for Costanera Center in Santiago, Chile"
author: "Cristian Gutierrez"
date: "21 de agosto de 2018"
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Developing Data Products-Week 2-Assignment
My First Map
Let's create a map that shows the Costanera Center in Santiago of Chile.
To do that, let's first load the library Leaflet.

```{r}
library(leaflet)
```

Create the map of Santiago, Chile.

```{r, eval=FALSE}
my_map <- leaflet() %>%
  addTiles()
my_map
```

Create a link to the office site of Costanera center, which we could get relevant information.
```{r}
CostaneraCenter <- c("<a href= 'http://mall.costaneracenter.cl/#map1' >Costanera Center</a>")
leaflet() %>%
  addTiles() %>%
  addMarkers(lat=-33.417993, lng=-70.606390, popup = CostaneraCenter)
```
Now if we click the blue icon on the map, it will display Costanera Center and the link.
